---
output: github_document
always_allow_html: yes
---

  <!-- README.md is generated from README.Rmd. Please edit that file -->


<!-- -->
<!-- FILL OUT OPTIONS !!! -->
<!-- -->
```{r scaffolding options, include=FALSE}
github_user_name   <- "petermeissner"
codecov_user_name  <- github_user_name
travis_user_name   <- github_user_name
appveyor_user_name <- github_user_name
```
<!-- -->
<!-- -->




```{r knitr options, echo = FALSE}
knitr::opts_chunk$set(
  fig.path = "man/figures/README-"
)
```


```{r r options, include=FALSE}
options("width"=110)

# get package info
tmp <- packageDescription( "dsmisc" )
#tmp <- packageDescription( basename(getwd()) )

package_name <- tmp$Package

```

```{r readme title, results='asis', echo=FALSE}
cat("#", tmp$Title)
```




**Status**


<a href="https://travis-ci.org/`r travis_user_name`/`r package_name`"><img src="https://api.travis-ci.org/`r github_user_name`/`r package_name`.svg?branch=master"><a/>
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/`r github_user_name`/`r package_name`?branch=master&svg=true)](https://ci.appveyor.com/project/`r github_user_name`/`r package_name`)
<a href="https://codecov.io/gh/`r github_user_name`/`r package_name`"><img src="https://codecov.io/gh/`r codecov_user_name`/`r package_name`/branch/master/graph/badge.svg" alt="Codecov" /></a>
<a href="https://cran.r-project.org/package=`r package_name`">
<img src="http://www.r-pkg.org/badges/version/`r package_name`">
</a>
<img src="http://cranlogs.r-pkg.org/badges/grand-total/`r package_name`">
<img src="http://cranlogs.r-pkg.org/badges/`r package_name`">






```{r, include=FALSE}
filelist.R   <- list.files("R", recursive = TRUE, pattern="\\.R$", ignore.case = TRUE, full.names = TRUE)
filelist.tests   <- list.files("tests", recursive = TRUE, pattern="\\.R$", ignore.case = TRUE, full.names = TRUE)
filelist.cpp <- list.files("src", recursive = TRUE, pattern="\\.cpp$", ignore.case = TRUE, full.names = TRUE)
lines.R      <- unlist(lapply(filelist.R, readLines))
lines.tests  <- unlist(lapply(filelist.tests, readLines))
lines.cpp    <- unlist(lapply(filelist.cpp, readLines))
length.R     <- length(grep("(^\\s*$)|(^\\s*#)|(^\\s*//)", lines.R,  value = TRUE, invert = TRUE))
length.tests <- length(grep("(^\\s*$)|(^\\s*#)|(^\\s*//)", lines.tests,  value = TRUE, invert = TRUE))
length.cpp   <- length(grep("(^\\s*$)|(^\\s*#)|(^\\s*//)", lines.cpp,  value = TRUE, invert = TRUE))
```


*lines of R code:* `r length.R`, *lines of test code:* `r length.tests`



**Version**

```{r, include=FALSE}
source_files <-
  grep(
    "/R/|/src/|/tests/",
    list.files(recursive = TRUE, full.names = TRUE),
    value = TRUE
  )
last_change <-
  as.character(
    format(max(file.info(source_files)$mtime), tz="UTC")
  )
```


```{r, results='asis', echo=FALSE}
cat(tmp$Version, "(",last_change,")")
```

**Description**


```{r, results='asis', echo=FALSE}
cat(tmp$Description)
```


**License**

```{r, results='asis', echo=FALSE}
cat(tmp$License, "<br>")
cat(tmp$Author)
```



**Citation**


```{r, results='asis', echo=FALSE}
cat("```r\n")
cat("citation(\"",package_name,"\")", sep = "")
cat("\n```\n")
```

```{r, results='asis', echo=FALSE}
cat("```r\n")
print_text <- capture.output(print(citation(package_name), style = "text"))
cat(gsub("_", "", print_text))
cat("\n```\n")
```


**BibTex for citing**

```{r, results='asis', echo=FALSE}
cat("```r\n")
cat("toBibtex(citation(\"",package_name,"\"))", sep = "")
cat("\n```\n")
```

```{r, results='asis', echo=FALSE}
cat("```\n")
cat(as.character(toBibtex(citation(package_name))), sep = "\n")
cat("\n```\n")
```



**Installation**

Stable version from CRAN:

```{r, results='asis', echo=FALSE}
cat("```r\n")
cat("install.packages(\"",package_name,"\")", sep = "")
cat("\n```\n")
```


<!-- Latest development version from Github: -->

<!-- ```{r, eval=FALSE} -->
<!-- devtools::install_github("user_name/repo_name") -->
<!-- ``` -->



## Usage



*starting up ...*
```{r}
library("dsmisc")
```






### Graph computations


*find isolated graphs / networks*


A graph described by an edgelist with two distinct subgraphs. 

```{r}
edges_df <- 
  data.frame(
    node_1 = c(1:5, 10:8),
    node_2 = c(2:6, 7,7,7)
  )

edges_df
```

Finding subgraphs and grouping them together via subgraph id. 

```{r}
edges_df$subgraph_id <- 
  graphs_find_subgraphs(
    id_1    = edges_df$node_1,
    id_2    = edges_df$node_2,
    verbose = 0
  )

edges_df
```


*speedtest for large graph*

```{r}
edges_df <- 
   data.frame(
    node_1 = sample(x = 1:10000, size = 10^5, replace = TRUE),
    node_2 = sample(x = 1:10000, size = 10^5, replace = TRUE)
  )

system.time({
  edges_df$subgraph_id <- 
    graphs_find_subgraphs(
      id_1    = edges_df$node_1,
      id_2    = edges_df$node_2,
      verbose = 0
    )
})
```



### Stats Functions

**Calculating the modus from a collection of values**

```{r}
# one modus only 
stats_modus(1:100)

# all values if multiple modi are found
stats_modus_multi(1:10)
```




### String Functions

{stringr} / {stringi} packages are cool ... but can they do this? 


**Extract specific RegEx groups**
```{r}
strings <- paste(LETTERS, seq_along(LETTERS), sep = "_")

# whole pattern
str_group_extract(strings, "([\\w])_(\\d+)")

# first group
str_group_extract(strings, "([\\w])_(\\d+)", 1)

# second group
str_group_extract(strings, "([\\w])_(\\d+)", 2)
```


### Data.Frame Manipulation

**Transform factor columns in a data.frame to character vectors**

```{r}
df <- 
  data.frame(
    a = 1:2, 
    b = factor(c("a", "b")), 
    c = as.character(letters[3:4]), 
    stringsAsFactors = FALSE
  )
vapply(df, class, "")

df_df <- df_defactorize(df)
vapply(df_df, class, "")
```



### Time Manipulation 

**File name ready time stamps**


```{r}
# current time
time_stamp()


time_stamp(
  ts  = as.POSIXct(c("2010-01-27 10:23:45", "2010-01-27 10:23:45")),
  sep = c("","_","")
)

time_stamp(
  ts  = as.POSIXct(c("2010-01-27 10:23:45", "2010-01-27 10:23:45")),
  sep = c("")
)
```



### Web Scraping 

**prepare multiple URLs via query parameter grid expansion**

```{r}
web_gen_param_list_expand(id=1:3, lang=c("en", "de"))
```

